---
layout: default
title: "Teaching and Outreach"
---

I find teaching and sharing my research with others immensely gratifying. In the past I have hosted R Coffee Hours and the corresponding [ThinkR website](../thinkR/) as a way of helping students working with R statistical software. Further, as most research is publicly funded, to some degree I consider outreach and education a social responsibility. I enjoy having discussions about research and sharing or inspiring exciting and interesting ideas. I also enjoy hearing about new and interesting ideas or concerns about research. I have, therefore, deliberately sought opportunities to both improve my teaching skills and share the results of my research with interested parties.

## Teaching & Outreach

#### Formal teaching

```{r}
tibble(dates = c(2025, 2023, 2023, 2022, "2021, 2022", paste("2021", "\u2013", "2022"), 2020, 2020, 2019, paste("2016", "\u2013", "2020")),
       content = c(
         paste("**MNS 191 Science Communication** (Guest Lecturer) University of Texas Marine Science Institute (Port Aransas, TX)"),
         paste("**MNS 354C Biology of Fishes** (Graduate Teaching Assistant) University of Texas Marine Science Institute (Port Aransas, TX)"),
         paste("**MNS 357 Marine Phytoplankton Diversity** (Graduate Teaching Assistant) University of Texas Marine Science Institute (Port Aransas, TX)"),
         paste("**MNS 352C Estuarine Ecology** (Graduate Teaching Assistant & Guest Lecturer) University of Texas Marine Science Institute (Port Aransas, TX)"),
         paste("**MNS 120L Field Methods in Marine Ecology** (Graduate Teaching Assistant) University of Texas Marine Science Institute (Port Aransas, TX)"),
         paste("**4-5 and 8th Grade Science** (Scientist-in-Residence Fellow) Port Aransas Independent School District (Port Aransas, TX)"),
         paste("**MNS 307 Introduction to Oceanography** (Graduate Teaching Assistant) University of Texas at Austin (Austin, TX)"),
         paste("**MNS 101 Seminar in Marine Science** (Graduate Teaching Assistant) University of Texas at Austin (Austin, TX)"),
         paste("**GEOL 100 Introduction to Geology** (Undergraduate Teaching Assistant) University of Pennsylvania (Philadelphia, PA)"),
         paste("**Biology, Ecology, Geology, Env. Sci., Physics, Spanish** (Peer Tutor) University of Pennsylvania (Philadelphia, PA)"))) %>%
  fmt_gt()
```

#### Pedagogical development

```{r}

tibble(dates = c(paste("2020", "\u2013", "2025"), paste("2021", "\u2013", "2025"), 2023, 2020),
       content = c(
         paste("**Concentration in Teaching and Mentoring** University of Texas at Austin (College of Natural Sciences)"),
         paste("**Advanced Teaching Preparation Certification** University of Texas at Austin (Center for Teaching & Learning)"),
         paste("**Inclusive Classrooms Leadership Certification** University of Texas at Austin (Division of Diversity & Community Engagement)"),
         paste("**GRS 097 Fundamentals of Teaching** University of Texas at Austin (Center for Teaching & Learning)"))) %>%
  fmt_gt()
```

#### Community service

```{r}
tibble(dates = c(paste("2024", "\u2013", "present"), paste("2021", "\u2013", "present"), 2025, 2025, 2024, paste("2023", "\u2013", "2024"), paste("2022", "\u2013", "2024"), paste("2022", "\u2013", "2024"), 2023, 2022, 2022, paste("2018", "\u2013", "2020"), paste("2018", "\u2013", "2020")),
       content = c(
         paste("**Letters to a Pre-Scientist** Pen Pal"),
         paste("**4/5 and 8th Grade Science Fair** Judge (Port Aransas Independent School District- Port Aransas, TX)"),
         paste("**Texas Bays and Estuaries Meeting** Volunteer (Port Aransas, TX)"),
         paste("**University of Texas Marine Science Institute Women in Marine Science Day** Volunteer (Port Aransas, TX)"),
         paste("**University of Texas Marine Science Institute Island Science Day** Volunteer (Port Aransas, TX)"),
         paste("**University of Texas at Austin STEM Girl Day** Volunteer (Austin, TX)"),
         paste("**Texas Bays and Estuaries Meeting** Planning Committee (Port Aransas, TX)"),
         paste("**University of Texas Marine Science Institute Summer Science Camp** Instructor (Port Aransas, TX)"),
         paste("**University of Texas at Austin Undergraduate Research Forum** Judge (Austin, TX)"),
         paste("**University of Texas at Austin Society for the Advancement of Gender Equity in STEM** Mentor (Austin, TX)"),
         paste("**Port Aransas Whooping Crane Festival** Volunteer (Port Aransas, TX)"),
         paste("**Independence Big Brothers Big Sisters** Mentor (Philadelphia, PA)"),
         paste("**West Philadelphia Tutoring Project** Volunteer (Philadelphia, PA)")
         )) %>%
  fmt_gt()
```

#### Undergraduate Mentoring

**2024** Sophia McKelvey, University of Texas at Austin Environmental Science Capstone Project\
**2023** Carole-Lynna Benhamou, University of Texas at Austin Environmental Science Capstone Project\
**2023** Malvika Patil, University of Texas at Austin Independent Research Project\
**2021-2022** Mona Birgisson, University of Texas Marine Science Institute Semester-by-the-Sea Research Project

{% if site.data.people %}

::: jumbotron
<h3>Students and Mentoring</h3>

<ul>

{% for student in site.data.people %}

<li>{{ student.name }}, {{ student.location }} ({{ student.degree }}, {{ student.year }})</li>

{% endfor %}

</ul>
:::

{% endif %}

:::: jumbotron
<h4>Sponsors</h4>

::: {style="display:block; text-align:center; margin-left:auto; margin-right:auto;"}
{% for funder in site.data.funders %}<a href="{{ funder.url }}" target="_blank"><img src="{{ site.url }}{{ site.baseurl }}/images/{{ funder.image }}" style="max-height: 80px; max-width: 200px; margin: 1%"/></a>{% endfor %}
:::
::::
